Intrusion Detection with \\ Genetic Algorithms and Fuzzy Logic

### 2013-12-02 Talk/Presentation.tex
Changed the theme, changed the determining the accuracy of an algorithm slide and the encoding of features and rules slide.

\mode<presentation>
{
  \usetheme{CambridgeUS}
  \setbeamercovered{transparent}
}

@@

\subsection{Determining the Accuracy of an Algorithm}
\begin{frame}
  \frametitle{Determining the Accuracy of an Algorithm}
\centering{Predicted}
\begin{table}
Actual
\begin{tabular}{l|ll}
 & Not Attack & Attack \\ \hline
Not Attack & True Negative (TN) & False Positive (FP) \\
Attack & False Negative (FN) & True Positive (FP)  \\
\end{tabular}
\end{table}
\linespace
	\begin{itemize}
		\item Detection rate (DR): the percentage of normal and attack activity correctly classified from the total number of data records.
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Encoding of Features and Rules}
	\begin{itemize}
	\item The four parameters are encoded into blocks. Each block is a feature with values between 0 and 7.
	\end{itemize}

\begin{figure}
\begin{tabular}{|cccc|} \hline
010 & 011 & 100 & 101\\
a=2 & b=3 & c=4 & d=5\\
\hline\end{tabular}
\end{figure}

	\begin{itemize}
	\item A rule has one block for each of 12 features followed at the end by a marker indicating the type of attack.
	\end{itemize}

\begin{figure}
\begin{small}
\begin{tabular}{|cccc|c|cccc|c|} \hline
010 & 011 & 100 & 101   & ...... & 010 & 011 & 101 & 111   & DoS\\
a=2 & b=3 & c=4 & d=5   & ...... & a=2 & b=3 & c=5 & d=7   &\\ 
    &     & Block 1&    &        &     & Block 12& &       & Type\\
\hline\end{tabular}
\caption{Based on [Jongsuebsuk-Wattanapongsakorn-Charnsripinyo, 2013]}
\end{small}
\end{figure}

>>>>

\mode<presentation>
{
  \usetheme{Frankfurt}
  \setbeamercovered{transparent}
  %\usecolortheme{whale}
}

@@

\subsection{Determining the Accuracy of an Algorithm}
\begin{frame}
  \frametitle{Determining the Accuracy of an Algorithm}
%\centering{Predicted}
\begin{table}
%Actual
Predicted
\begin{tabular}{l|ll}
Actual   & Not Attack & Attack \\ \hline
Not Attack & True Negative (TN) & False Positive (FP) \\
Attack & False Negative (FN) & True Positive (FP)  \\
\end{tabular}
\end{table}
\linespace
	\begin{itemize}
		\item Detection rate (DR): the percentage of normal and attack activity correctly classified from the total number of data records.
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Encoding of Features and Rules}
	\begin{itemize}
	\item The four parameters are encoded into blocks. Each block is a feature with values between 0 and 7.
%	\end{itemize}

%\begin{figure}
%\begin{tabular}{|cccc|} \hline
%010 & 011 & 100 & 101\\
%a=2 & b=3 & c=4 & d=5\\
%\hline\end{tabular}
%\end{figure}

%	\begin{itemize}
	\item A rule has one block for each of 12 features followed at the end by a marker indicating the type of attack.
	\end{itemize}

\begin{figure}
\begin{small}
\begin{tabular}{|cccc|c|cccc|c|} \hline
010 & 011 & 100 & 101   & ...... & 010 & 011 & 101 & 111   & DoS\\
a=2 & b=3 & c=4 & d=5   & ...... & a=2 & b=3 & c=5 & d=7   &\\ 
    &     & Block 1&    &        &     & Block 12& &       & Type\\
\hline\end{tabular}
\caption{Based on [Jongsuebsuk \emph{et al.}, 2013]}
\end{small}
\end{figure}
